The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-10 manuscript/5pillars.Rmd
Complete key points and bio

* Irreproducibility of bioinformatics studies remains a significant problem.

@@

**Pierre Poulain** is an Associate Professor at Université Paris Cité, Institut Jacques Monod, France.
Research directions include proteomics, bioinformatics and education/pedagogy.

>>>>

* Irreproducibility of bioinformatics studies remains a significant and still relevant problem.

@@

**Pierre Poulain** is an Associate Professor at Université Paris Cité, Institut Jacques Monod, France.
Research directions include bioinformatics, large scale data analysis and education/pedagogy.
